On existence of integral point sets and their diameter bounds \footnote{ This work was carried out at Voronezh State University and supported by the Russian Science Foundation grant 19-11-00197. }

### 2020-01-04 pps-linear-bound/pps-linear-lower-bound.tex
[J220] Review 2, minor remark 3
Reformulaton and a brief proof
[J220] Review 2, medium remark 8

Now we need to estimate $\varphi_n$ with $\beta/\sqrt{n-n_0}$.
Using the upper bound of Theorem~\ref{thm:varphi_k_bounds},
one can easily find the values of $\beta$ and $n_0$.

@@

@@

Using the ``blowing up'' procedure described in~\cite[Theorem 1.3]{kurz2008bounds},
we can construct an integral point set $M$ in $m$-dimensional Euclidean space, $m\geq 3$,
with distance 1 occuring in it.
If we have an integral point set with distance 1 occuring,
then we can easily dilate it to turn 1 into the desired distance.
These facts, together with Theorem~\ref{thm:minimeter_1_planar}, give the following theorem.

@@

\begin{proof}
	Take a facher integral point set according to Construction~\ref{con:planar_set_with_minimeter_1}
	with sufficiently large height and then apply the ``blowing up'' procedure described in~\cite[Theorem 1.3]{kurz2008bounds},
	replacing the point that is not situated on the line, with an $(m-2)$-dimensional simplex of proper side length.
	That simplex will consist of $m-1$ points;
	we can exclude practically all $M_J$ points, except the two points with distance 1.
	So, the set consists of $m+1$ or more points and has distance 1 occuring in it.
	As distance 1 occurs in the obtained set, it is prime.
\end{proof}

>>>>

Now we will use the upper bound of Theorem~\ref{thm:varphi_k_bounds}
to estimate $\varphi_n$ with $\beta/\sqrt{n-2}$.

@@

\begin{proof}
	Indeed, for $n \geq 21492$ we have
	\begin{multline*}
		\varphi_n
		\leq
		\varphi_{n-1}
		\leq
		\frac{1}{n-2} +
		\sqrt{
			\frac{1}{(n-2)^2}
			+
			\frac{2}{(n-2)\sqrt{3}}
		}
		=
		\\=
		\frac{1}{\sqrt{n-2}}
		\cdot
		\frac{1}{\sqrt{n-2}}
		 +
		\sqrt{
			\frac{1}{(n-2)^2}
			+
			\frac{2}{(n-2)\sqrt{3}}
		}
		\leq
		\\ \leq
		\frac{1}{\sqrt{n-2}}
		\cdot
		\frac{1}{\sqrt{21490}}
		 +
		\sqrt{
			\frac{1}{(n-2)^2}
			+
			\frac{2}{(n-2)\sqrt{3}}
		}
		=
		\\=
		\frac{1}{\sqrt{n-2}}
		\left(
		\frac{1}{\sqrt{21490}}
		 +
		\sqrt{
			\frac{1}{n-2}
			+
			\frac{2}{\sqrt{3}}
		}
		\right)
		\leq
		\\ \leq
		\frac{1}{\sqrt{n-2}}
		\left(
		\frac{1}{\sqrt{21490}}
		 +
		\sqrt{
			\frac{1}{21490}
			+
			\frac{2}{\sqrt{3}}
		}
		\;
		\right)
		.
	\end{multline*}
\end{proof}

@@

To build integral points sets with distance 1 in higher dimensions,
we need the ``blowing up'' procedure described in~\cite[Theorem 1.3]{kurz2008bounds}.

\begin{construction}
	\label{con:blowing_up}
	Let $M\in\mathfrak{M}(2,n)$ have many points on a straight line $l_1$
	and $M\setminus l_1 \subset l_2$ for a straight line $l_2$.
	Moreover, let $l_1$ be parallel to $l_2$.

	Construct $M' \subset \mathbb{R}^m$ by replacing all the points $M_1,...,M_n\in M \cap l_2$
	by equal $(m-2)$--dimensional simplices $S_1,...,S_n$
	in such a way that
	\begin{equation}
		\forall(j=1,...,n) \forall(N_i \in M \cap l_1 )\forall\left(M^j_k, M^j_h \in S_j\right)\left[|N_i M^j_k| = |N_i M^j_h|\right].
	\end{equation}
	Then under certain conditions (in particular, if $\#(M \cap l_2)=1$ that we actually need)
	we get $M'\in\mathfrak{M}(m,\mathbb{N})$.

	For further examples we also refer the reader to~\cite{avdeev2019particular}.
\end{construction}

Now we can construct an integral point set $M$ in $m$-dimensional Euclidean space, $m\geq 3$,
with distance 1 occuring in it.
If we have an integral point set with distance 1 occuring,
then we can easily dilate it to turn 1 into the desired distance.
These facts, together with Theorem~\ref{thm:minimeter_1_planar}, give the following theorem.

@@

\begin{proof}
	Take a facher integral point set according to Construction~\ref{con:planar_set_with_minimeter_1}
	with sufficiently large height and then apply the ``blowing up'' procedure described in Construction~\ref{con:blowing_up},
	replacing the point that is not situated on the line, with an $(m-2)$-dimensional simplex of proper side length.
	That simplex will consist of $m-1$ points;
	we can exclude practically all $M_J$ points, except the two points with distance 1.
	So, the set consists of $m+1$ or more points and has distance 1 occuring in it.
	As distance 1 occurs in the obtained set, it is prime.
\end{proof}
